---
title: "R Notebook"
output: html_notebook
---

# Simple bayesian problem 1

| Given a fair coin what is the prob of observing 5 H in 5 trials

= (no of ways of getting 5 H)/total no of possible ways or outcomes

= (1)/(2^5)

= 1/32

= 0.03125

This is also equal to 
p(x) = choose(n, x) p^x (1-p)^(n-x)

p(x) = 1 * (0.5)^5 * (0.5) ^ (5-5)
```{r}
dbinom(x = 5, size=5, prob=0.5)
```
Also

10,000 sims of 5 coins at a time wit each having a 0.5 prob : No of them turning 5 is roughly the same
```{r}
sum(rbinom(10000, 5, 0.5)==5)/10000

```




## prob 2

Prob of getting exactly 4 H in 5 trials

= (no of ways of getting exactly 4H and 1 T)/total no of possible ways or outcomes

= select any 4 trails to yield H/32

= (5C4)/32

= 5/32

=0.15625

```{r}
dbinom(x = 4L, size=5, prob=0.5)
```

```{r}
sum(rbinom(10000, size=5, prob=0.5)==4)/10000
```


## prob 3 

| Given a bag of 1B, and 3 W marbels, what is the prob of observing 1B, 1W, 1B marbels with 3 random picking with replacements.

= ways of getting 1 B + 1 W + 1B / total no of ways or outcome possible

= (3)/4^3

=5/64

=0.046875

```{r}
n <- 1000000
n
```


```{r}
sum((rbinom(n, 1, 0.25) * rbinom(n, 1, 0.75) * rbinom(n, 1, 0.25))==1)/n
```

## prob 3 

| Given a bag of 2B, and 3 W marbels, what is the prob of observing 1B, 1W, 1B marbels with 3 random picking with replacements.

= (ways of selecting 1B * ways of selecting 1W * ways of selecting 1B)/total no of outcomes possible

 = (2 * 2 * 2)/4^3
 
 = 8/64
 
 =0.125

simulations

```{r}
sum((rbinom(n, size=1, 0.5) * rbinom(n, size=1, prob=0.5) * rbinom(n, size=1, prob=0.5))==1)/n
```

